\documentclass[10pt, onecolumn, draftclsnofoot, letterpaper, compsoc]{IEEEtran}

\usepackage{listings}

\title{Meeting Minutes \#1:\\ Introductions + Code3 Visionary Overview}
\author{
	\textit{October 5th, 2017}}

\begin{document}

\maketitle

\section{Attendees}
Ofer Heyman\\
Carl Niedner\\
Chester Ornes\\
Kien Tran\\
Brian Wiltse\\
\section{Meeting Type}
Face-to-Face
\section{Summary}
This was an introductory meeting for Brian and Kien to get to know the team as well as learn about the organization. 
The meeting introduces what the Code3 Visionary project is about, and sets the expectation for both the developers and students. 
Brian and Kien were also given a warm-up project to work on and is expected to get back to Carl about completion dates. 
The NDAs were given out and signed by both students before leaving.
\section{Action Items}
    \begin{itemize}
        \item Brian and Kien will establish an estimation of when the warm-up project is to be completed and send estimation to Carl Niedner by Tuesday October 10, 2017.

        \item Carl Niedner will send 2 files (Actual Data and Generated Predicted Data) to Kien and Brian by Tuesday October 10, 2017.

        \item Kien and Brian will individually draft and finalize problem / solution statements that will be sent to Carl Niedner for email verification to satisfy Capstone Course Objectives. 
        Email verification of satisfactory completion by the client will be due on Friday October 20, 2017.
    \end{itemize}
\end{document}
