\documentclass[10pt, onecolumn, draftclsnofoot, letterpaper, compsoc]{IEEEtran}

\usepackage{listings}

\title{Meeting Minutes \#2:\\ Warmup Assessment, Requirements Document, New mini-project}
\author{
	\textit{October 24th, 2017}}

\begin{document}

\maketitle
\section{Time/Date}
1:30pm, October 24th, 2017
\section{Attendees}
Carl Niedner\\
Chester Ornes\\
Kien Tran\\
Brian Wiltse\\
\section{Meeting Type}
Face-to-Face
\section{Summary}
This is the second meeting for Kien and Brian with the Levrum team. 
The meeting began with Kien and Brian showing their work on the WarmUp project that was finished. 
They walked through the code and showed the program running with the output text file to make sure that it was to the expectation of Carl and Chester. 
Further improvements to the program was mentioned such as changing the output to be compatible with Excel. 
Afterward, the team talked about the upcoming Requirements document. 
Carl and Chester went over the project detailing the key points that they envision. 
Due to this project being new, much of the information will come as the team progress. 
For now, the 3 main components discussed were data input (which includes data ingestion, feature extraction and data exploration), machine learning algorithm, and creating a minimalistic user interface (UI). 
Further explanation into these components will come as the team progress through the project. 
The last portion was discussing about Kien and Brian's next mini-project. 
Carl and Chester gave an overview of what the next project was about and wants the capstone team to work on it as well as give them a deliverable date.
\section{Action Items}
    \begin{itemize}
        \item Kien and Brian will establish an estimated time of when the next mini-project is to be completed and send estimation to Carl.
        \item Carl will create a Github account to be added on to the capstone repository. \textbf{DONE}
        \item Kien and Brian will work on the Requirements document and send a rough draft to Carl for review and feedback.
    \end{itemize}
\end{document}
