\documentclass[10pt, onecolumn, draftclsnofoot, letterpaper, compsoc]{IEEEtran}

\usepackage{listings}

\title{Meeting Minutes \#3:\\ US Census Review, Next Project Update, Technology Document Questions}
\author{
	\textit{November 16, 2017}}

\begin{document}

\maketitle
\section{Attendees}
Carl Niedner\\
Chester Ornes\\
Kien Tran\\
Brian Wiltse\\

\textbf{Meeting Type:} Face-to-Face

\textbf{Location:} Levrum downtown office

\textbf{Time:} 10:30am ~ 11:30am

\section{Summary}
In today's meeting we went over the US Census project Brian and Kien have been working on and gave Carl and Chester and rundown of how our program worked and what the API calls looked like. 
Carl and Chester were impress with the progress and propose the next phase is to use census tract with appropriate shapefile to create a program that would allow the user to get information about the area around their desire location. 
Finally, Brian and Kien were able to ask questions about their Technology Review document.
\section{Action Items}
    \begin{itemize}
        \item Brian and Kien must research on US Census Tract and if there is a way to retrieve that information. 
They must also look into shapefile and how to create this program for the team. 
For now, the scope will just be in Charloete, NC. 
They will report back to Carl what they have found by the next meeting.
        \item Chester will be sending to Brian and Kien a csv file that they created a while ago that can be use as an example.
    \end{itemize}
\end{document}
